A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex
minor

\subsection{Super Yang--Mills Theory: pure gauge theory}
\label{sect:gaugemultipletSUSY}

@@

Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.  The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.  To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang--Mills Theory} \label{sect:2d(2,2)}
First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.  
%This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$. \brian{Not sure what $(a^{-1},b^{-1})$ means? Do you mean $(-a,-b)$?}

>>>>

\subsection{Super Yang--Mills Theory: Pure Gauge Theory}
\label{sect:gaugemultipletSUSY}

@@

Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.  The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.  To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang--Mills Theory} \label{sect:2d(2,2)}
First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.  
%This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (-a, -b)$.
